Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated

### 2017-03-11 ms_pre_post.Rmd
Final edits

@@

>>>>

<!--- Is this really correct? Degeneracy is defined by different processes having the same effect, so I don't think pre- and post-copulatory inbreeding avoidance are *affected by* degeneracy so much as *characterised by*, or *an example of* degeneracy. --->

@@

<!--- Something doesn't seem quite right here. Our model doesn't provide support for the verbal hypothesis in the same way that real data would. Perhaps it *clarifies* the verbal hypothesis, *formalises?* --->
